An analysis of a single basketball game

### 2022-06-02 inst/NBA.Rmd
minor changes

--
title: "Basketball: an analysis of a single game"
output: html_document
---

@@

for(i in seq_len(nrow(NBA_table))){
  if(scored[i] == 'W'){  # Warriors score a point
    onpitch_scored  <- names(which(W_onpitch[i,]))
    onpitch_noscore <- names(which(C_onpitch[i,]))
  } else if(scored[i] == "C"){ # Cleveland score a point
    onpitch_scored  <- names(which(C_onpitch[i,]))
    onpitch_noscore <- names(which(W_onpitch[i,]))
  } else {
    stop("scorint team must be either W or C")
  }
  print(onpitch_scored)
  print(onpitch_noscore)
  if(possession[i] == 'W'){
    onpitch_scored1 <- c(onpitch_scored,"possession")
    onpitch_scored2 <- c(onpitch_scored,"W_possession")
  } else if (possession[i] == 'C'){
    onpitch_scored1 <- c(onpitch_scored,"possession")
    onpitch_scored2 <- c(onpitch_scored,"C_possession")
  } else {
    stop("possession must be either W or C")
  }

>>>>

---
title: "An analysis of a single basketball game"
output: html_document
---

@@

for(i in seq_len(nrow(NBA_table))){
  if(scored[i] == 'W'){  # Warriors score a point
    onpitch_scored  <- names(which(W_onpitch[i,]))
    onpitch_noscore <- names(which(C_onpitch[i,]))
  } else if(scored[i] == "C"){ # Cleveland score a point
    onpitch_scored  <- names(which(C_onpitch[i,]))
    onpitch_noscore <- names(which(W_onpitch[i,]))
  } else {
    stop("scorint team must be either W or C")
  }
  if(possession[i] == 'W'){
    onpitch_scored1 <- c(onpitch_scored,"possession")
    onpitch_scored2 <- c(onpitch_scored,"W_possession")
  } else if (possession[i] == 'C'){
    onpitch_scored1 <- c(onpitch_scored,"possession")
    onpitch_scored2 <- c(onpitch_scored,"C_possession")
  } else {
    stop("possession must be either W or C")
  }
